data_cleaning_longer_period

### 2023-08-16 code/analysis_Redo.Rmd
updated to better sample

splits <- quantile(dfc[dfc$Year == 2010,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_revenue, c(0.33, 0.66), na.rm = TRUE)

@@

df.profit <- df.profit %>% 
  left_join(dfc %>% filter(Year == 2010) %>% select(ID, ngla_net_gain_loss, ngla_revenue, ngla_expense, Assets, Pct.NHA:Pct.COM) %>% 
  mutate(pc = ngla_net_gain_loss / ngla_revenue) , by = c("ID")) %>% 
  filter(`BHCMIS ID` %notin% c("010450","0438280","070430"))

@@

splits1 <- c(min(df.profit$pc, na.rm = TRUE), splits)
splits2 <- c(splits, max(df.profit$pc, na.rm = TRUE))

@@

  df.temp <- df.profit[,c(1:9, j, 13:ncol(df.profit))] 
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp %>% filter(pc >= splits1[g] & pc <= splits2[g]), 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

@@

data.frame(Subset = c(rep("Low", 3), rep("Medium", 3), rep("High", 3)),
      Outcome = rep(c("Total","Quality","Financial"), 3),
      Estimate = as.numeric(did.profit[,1]), 
      SD = as.numeric(did.profit[,2]))

@@

@@

did2s(
      data = dfc.new %>% 
        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.08 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
      yname = "Total", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

>>>>

splits <- quantile(dfc[dfc$Year == 2010,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_expense, c(0.33, 0.66), na.rm = TRUE)

@@

df.profit <- df.profit %>% 
  left_join(dfc %>% filter(Year == 2010) %>% select(ID, ngla_net_gain_loss, ngla_revenue, ngla_expense, Assets, Pct.NHA:Pct.COM) %>% 
  mutate(pc = ngla_net_gain_loss / ngla_expense) , by = c("ID")) %>% 
  filter(`BHCMIS ID` %notin% c("010450","070430"))

@@

splits1 <- c(min(df.profit$pc, na.rm = TRUE)-1, splits)
splits2 <- c(splits, max(df.profit$pc, na.rm = TRUE))

@@

  df.temp <- df.profit[,c(1:9, j, 13:ncol(df.profit))] 
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp %>% filter(pc > splits1[g] & pc <= splits2[g]), 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

@@

data.frame(Subset = c(rep("01Low", 3), rep("02Medium", 3), rep("03High", 3)),
      Outcome = rep(c("Total","Quality","Financial"), 3),
      Estimate = as.numeric(did.profit[,1]), 
      SD = as.numeric(did.profit[,2])) %>% 
  mutate(Subset.f = as.factor(Subset)) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ggtitle("DID Estimates by Baseline Profitiability")

@@

splits <- quantile(dfc[dfc$Year == 2010,]$Total, c(0.5), na.rm = TRUE)

df.size <- dfc %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100,

df.size <- df.size %>% 
  left_join(dfc %>% filter(Year == 2010) %>% select(ID, Total, Pct.NHA:Pct.COM) %>% 
  rename(Size = Total) , by = c("ID")) %>% 
  filter(`BHCMIS ID` %notin% c("010450","070430"))

splits1 <- c(min(df.size$Size, na.rm = TRUE), splits)
splits2 <- c(splits, max(df.size$Size, na.rm = TRUE)+1)

did.size <- c(0, 0, 0, 0)
for (g in 1:2){
  for (j in 10:12){

  df.temp <- df.size[,c(1:9, j, 13:ncol(df.size))] 
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp %>% filter(Size >= splits1[g] & Size < splits2[g]), 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

  did.size <- rbind(did.size, outcomes$coeftable)

did.size <- did.size[-1,]
rownames(did.size) <- NULL

data.frame(Subset = c(rep("01Below", 3), rep("02Above", 3)),
      Outcome = rep(c("Total","Quality","Financial"), 2),
      Estimate = as.numeric(did.size[,1]), 
      SD = as.numeric(did.size[,2])) %>% 
  mutate(Subset.f = as.factor(Subset)) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.96, xmax = Estimate + SD * 1.96)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ggtitle("DID Estimates by Baseline Clinics Size")
```

@@

did2s(
      data = dfc.new %>% 
        inner_join(dfc %>% filter(Year == 2010 & Total < 14000 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
      yname = "Altman", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

### 2023-08-16 code/data_cleaning_longer.Rmd
updated to better sample

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  filter(`2010` == 1 & `2011` == 1 ) %>%   
  #filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2021`) %>% 
  pivot_longer(cols = c(`2010`:`2021`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

@@

vec.atts <- rep(c(2012:2021), (table(comp.initial$Att) / 12)[-1])

>>>>

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  filter(`2010` == 1 & `2011` == 1 & `2012` == 1) %>%   
  #filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2021`) %>% 
  pivot_longer(cols = c(`2010`:`2021`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

@@

vec.atts <- rep(c(2013:2021), (table(comp.initial$Att) / 12)[-1])
